Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-01 ms.tex
Mention best response from a dish antenna
From dbca120:
============

In ms.tex,

(*) Add a sentence on dish-shaped yielding best response in the section
on wide-field effects
(*) Minor change to a sentence in the Results section

\citet{thy15} have described in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}. Here, we give a brief overview of the wide-field signature predicted therein.

@@

Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal. Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot presented in their study, the high level of thermal noise prevented a robust confirmation. In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.

@@

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise added (bottom), for reference. The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent. We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.

>>>>

\citet{thy15} have described in detail the effects of wide-field measurements as seen in the delay spectra of interferometer {\it visibilities}. Here, we list the relevant equations and give a brief overview of the wide-field signatures predicted therein.

@@

Detailed modeling presented in \citet{thy15} has shown this feature to be a leading source of contamination of the Fourier modes most sensitive to the EoR H~{\sc i} signal. And a dish-shaped antenna is found to yield the most desirable response from a foreground contamination viewpoint. Although there is marginal evidence for presence of this feature in the {\it zenith} snapshot used in their study, the high level of thermal noise prevented a robust confirmation. In this paper, we confirm the {\it pitchfork} signature using deeper data from the MWA.

@@

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling \citep{thy15} with no thermal noise fluctuations (bottom), for reference. The dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top) similar to the one used in \citet{thy15}, and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) has become $\gtrsim 10$ times more prominent. We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
